---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TimeGPTapi

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html) [![devel version](https://img.shields.io/badge/devel%20version-0.1.0-blue.svg)](https://github.com/daniGiro/TimeGPTapi) [![License: GPL-3](https://img.shields.io/badge/license-GPL--3-forestgreen.svg)](https://cran.r-project.org/web/licenses/GPL-3)
<!-- badges: end -->

`TimeGPT` is a generative pre-trained transformer model for time series analysis  ([https://docs.nixtla.io/docs](docs.nixtla.io/docs)) developed by **Nixtla** ([https://nixtla.io](https://nixtla.io)). It was trained on the largest collection of public time series and can predict the future values of a single time series based on the provided. This R package provides an R interface to interact with the `TimeGPT API`.


## Installation

You can install the development version of TimeGPTapi from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("danigiro/TimeGPTapi")
```

## Quickstart

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library(TimeGPTapi)

# Loading the air passengers dataset and the time vector
y <- AirPassengers
time_air <- zoo::as.Date(AirPassengers)

# Set the TimeGPT API token
set_TimeGPT_token("<TIMEGPT_TOKEN>")
obj <- TimeGPT(AirPassengers, time_air, freq = "M", verbose = TRUE, historic = TRUE)

# Forecasting the next 12 horizons using TimeGPT
fore <- forecast(obj2, h = 12)
```

## TODO

- [ ] Implement external regressor (`xreg`)
- [ ] Multivariate TimeGPT

## Copyright

This R package is released under the *GNU General Public License v3.0*. The `TimeGPT` model and `API` are proprietary technologies developed by **Nixtla**, and all rights are reserved. The use of the `TimeGPT API` is subject to Nixtla's terms and conditions, which can be found at [https://nixtla.io](https://nixtla.io).
